Source Summaries

### 2020-04-06 paper/sourceSummaries/summary7.tex

\noindent
\subsection{Title}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
%\bibentry{filizzola2018security}

@@

\noindent
Main Idea

@@

\noindent
Theory

@@

\noindent
Method

@@

\noindent
Findings

@@

\noindent
Future Directions

>>>>

\noindent
\subsection{{O}n {B}ad {R}andomness and {C}loning of {C}ontactless {P}ayment and {B}uilding {S}mart {C}ards}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{6565237}

@@

\noindent
The authors describe the problems with the Mifare Classic RFID card's random number generator and examine the real life implications of bad key generation.

@@

\noindent
Game Theory.  The authors explore the possibility of directly attacking MiFare cards, through the Random Number Generator and otherwise.

@@

\noindent
The authors review recent revelations about MiFare random number generation and describe the problem with entropy.  They then review the probability distribution of the random number generators for Mifare cards.

@@

\noindent
The authors found that random number generators in small cards like the Mifare are often not secure.  They found that using problems in random number generators allow for very easily breaking security in many smart cards.

@@

\noindent
The authors do not describe any formal future directions, but one obvious future direction would be doing research on more vendors of smart cards.
